Manuscript

### 2015-06-29 inst/simulation/manuscript.Rmd
...

boundaryDF <- ggplot2::fortify(FinlandWTCStudy(context=context, response="canis.lupus")$studyArea$boundary)
cutoff <- c(1,1000)
```

@@

for (scenario in scenarios) {
  mss <- getMSS(scenario, nSurveyRoutes=500)
  study <- mss$study
  tracks <- study$loadTracks(iteration=iterations[i])
  intersections <- tracks$countIntersections(surveyRoutes=mss$surveyRoutes, save=F)

@@

  #trackData$type <- "track"
  #surveyRoutesData$type <- "transect"
  #x <- rbind(trackData[,c("long","lat","order","piece","group","observation","type")], surveyRoutesData[,c("long","lat","order","piece","group","observation","type")])
  #x$colour <- factor(paste(x$type, x$observation))
  #ggplot(x, aes(long, lat, group=group, colour=colour)) + geom_path()

@@

#window <- c(3.375, 3.4, 6.9, 6.925)*1e6
window <- (c(3.425, 3.45, 6.95, 6.975)+c(-.01,.01,-.01,.01)*9)*1e6
habitatRaster <- crop(study$studyArea$habitat, extent(window))
z <- sampleRegular(habitatRaster, 10000, asRaster=TRUE)
habitatData <- as.data.frame(rasterToPoints(z))
#habitatData <- as.data.frame(rasterToPoints(habitatRaster))
colnames(habitatData) <- c("x","y","z")
habitatData$scenario <- factor("E", levels=scenarios)
habitatData2 <- habitatData
habitatData2$scenario <- factor("F", levels=scenarios)
habitatData <- rbind(habitatData, habitatData2)

@@

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.4) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray55","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_raster(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
#print(p)
#saveFigure(p, "manuscript-figure-1.png", width=8, height=5)
saveFigure(p, "manuscript-figure-1.png", width=17, height=15, dpi=200) # draft quality

@@

```{r figure-1-separate, eval=FALSE}
getRaster <- function(habitatRaster, xlim, ylim, size=10000) {
  x <- crop(habitatRaster, extent(c(xlim, ylim)))
  y <- sampleRegular(x, size=size, asRaster=TRUE)
  habitatData <- as.data.frame(rasterToPoints(y))
  colnames(habitatData) <- c("x","y","z")
  habitatData$z <- factor(habitatData$z, levels=0:255)
  col <- habitatRaster@legend@colortable
  names(col) <- 0:255
  return(habitatData)
}

getPanel <- function(scenario, xlim=c(3.375,3.4)*1e6, ylim=c(6.9,6.925)*1e6, habitatRaster, trackData, surveyRoutesData) {
  s <- scenario
  p <- if (!missing(habitatRaster)) {
    habitatData <- getRaster(habitatRaster=habitatRaster, xlim=xlim, ylim=ylim)
    ggplot(habitatData) + geom_raster(aes(x, y, fill=z)) + scale_fill_manual(values=col) +
      geom_path(data=subset(trackData, scenario==s), aes(long, lat, group=group, colour=observation))
  }
  else {
     ggplot(subset(trackData, scenario==s)) +
       geom_path(aes(long, lat, group=group, colour=observation))
  }

  p <- p + scale_colour_manual(values=c("gray40","black")) +
    geom_path(data=subset(surveyRoutesData, scenario==s), aes(long, lat, group=group)) +
    coord_fixed(ratio=1, xlim=xlim, ylim=ylim) +
    theme_raster(base_size=10, panel.border=element_rect(fill="transparent"), plot.title=element_text(size=12)) +
    ggtitle(s)

library(gridExtra)

p1 <- getPanel(scenario="A", trackData=trackData, surveyRoutesData=surveyRoutesData)
p2 <- getPanel(scenario="B", trackData=trackData, surveyRoutesData=surveyRoutesData)
p3 <- getPanel(scenario="C", trackData=trackData, surveyRoutesData=surveyRoutesData)
p4 <- getPanel(scenario="D", trackData=trackData, surveyRoutesData=surveyRoutesData)
p5 <- getPanel(scenario="E", habitatRaster=study$studyArea$habitat, trackData=trackData, surveyRoutesData=surveyRoutesData)
p6 <- getPanel(scenario="F", habitatRaster=study$studyArea$habitat, trackData=trackData, surveyRoutesData=surveyRoutesData)
p <- arrangeGrob(p1, p2, p3, p4, p5, p6, ncol=3, nrow=2)
saveFigure(p, "manuscript-figure-1.png")
```

@@

#x<-data.frame(scenario="C", iteration=as.integer(3), stringsAsFactors=F)
getAgentLocations = function(scenarios, modelName, iterations, years) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, years) {

    #study <- getStudy(scenario=x$scenario)
    #intersections <- study$loadIntersections(iteration=x$iteration)
    #observationTracks <- SimulatedTracks$new(study=study, iteration=x$iteration)
    #observationTracks$loadTracks(fileName=observationTracks$getObservationTracksFileName(), addColumns=TRUE)
    # TODO: use observation tracks ^^^^

    study <- getStudy(scenario=x$scenario)
    tracks <- study$loadTracks(iteration=x$iteration)
    tracks$tracks <- subset(tracks$tracks, year %in% years & yday<59)
    intersections <- study$loadIntersections(iteration=x$iteration)

@@

    #d_ply(observationTracks$tracks, .(id, year, burst), function(x) {
    #  with(x[1,], message(id, " ", year, " ", burst))
    #})

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE, weightHabitats=F) {
  ddply(data.frame(scenario=scenarios, year=rep(year, length(scenarios)), iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    withHabitatWeights <- if (weightHabitats && substr(x$scenario, 1, 1) %in% c("E","F")) T else F
    study <- getStudy(scenario=x$scenario, withHabitatWeights=withHabitatWeights)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()
    estimates$data <- subset(estimates$data, year == x$year)
    #studyArea <- FinlandStudyArea$new(context=context)$setup(tolerance=0.001)
    #density <- estimates$getPopulationDensityInterpolate(getSD=sd, maskPolygon=studyArea$boundary)

    #habitatWeights <- study$getHabitatWeights(iteration=x$iteration)
    #density <- estimates$getPopulationDensity(habitatWeights=habitatWeights, .parallel=T)
    density <- estimates$getPopulationDensity(.parallel=T)
    density <- if (withHabitatWeights) {
      habitatWeights <- study$getHabitatWeights(iteration=x$iteration)
      habitatWeightsRaster <- habitatWeights$getWeightsRaster(save=F)
      density$weight(habitatWeightsRaster)
    } else wdensity <- density$copy()

    #density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- x$year

    return(density)
  }, modelName=modelName, sd=sd)
}
#iterations <- as.integer(c(1,4,1,2,5,31))
#densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, sd=F, log=F)

@@

p1 <- ggplot(wdensitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(data=densitiesScaled, aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2)))), trans="log10",
                       #breaks=c(10^-4.5, 10^-4, 10^-3.5, 10^-3, 10^-2.5),
                       breaks=trans_breaks("log10", function(x) 10^x),
                       #labels=c(expression(10^-4.5), expression(10^-4.0), expression(10^-3.5), expression(10^-3.0), expression(10^-2.5)), limits=c(10^-4.5, 10^-2.5)
                       labels=trans_format("log10", math_format(10^.x))
                       ) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) +
  theme(legend.position="bottom", legend.margin=unit(-2, units="line"), legend.title=element_text(size=10), legend.text=element_text(size=10),
        plot.margin=unit(c(-3, 0, 0, -.5), units="line")) #top, right, bottom, and left margins
g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g1, "manuscript-figure-2a.png", width=17, height=8.8, dpi=200) # draft quality
saveFigure(g1, "manuscript-figure-2a.pdf", width=17, height=8.8, dpi=300)

p2 <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0.01,0.01)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() +
  theme(panel.grid.major=element_line(colour="grey"),
        plot.margin=unit(c(0, 0, 0, -.5), units="line")) #top, right, bottom, and left margins
g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g2, "manuscript-figure-2b.png", width=17, height=6.9, dpi=200) # draft quality
saveFigure(g2, "manuscript-figure-2b.pdf", width=17, height=6.9, dpi=300)

p <- arrangeGrob(g1, g2)
saveFigure(p, "manuscript-figure-2.png", width=17, height=17, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-2.pdf", width=17, height=17, dpi=300)

@@

getPopulationSizes <- function(scenarios, modelNames, populationSizeCutoff=Inf) {
  study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
  validation <- Validation(study=study, populationSizeCutoff=populationSizeCutoff)
  populationSizes <- validation$getValidationTemporalPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  #validation$summarizePopulationSize(populationSizes)  
}

@@

populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames[c(1,3,4,5)])
#populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,4,5)])
#populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,4,5)])

meanPopulationSizes  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[c(1,3,5)]))
logPopulationSizes <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[c(1,3,5)]))
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

#meanPopulationSizes2000  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff, models=modelNames[c(1,3,5)]))
#logPopulationSizes2000 <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes2000, 10*cutoff, models=modelNames[c(1,3,5)]))
#logMeanPopulationSizes2000  <- getMeanPopulationSizes(logPopulationSizes2000)

#meanPopulationSizes10Days  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff, models=modelNames[c(1,3,5)]))
#logPopulationSizes10Days <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes10Days, cutoff, models=modelNames[c(1,3,5)]))
#logMeanPopulationSizes10Days  <- getMeanPopulationSizes(logPopulationSizes10Days)
```

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, models, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate, models) {
    xrows <- nrow(x)
    old <- x
    x <- cutoffPopulationSizes(x, overEstimate, models=models)
    if (nrow(x) == 0) {
      print(old)
      stop("ERROR")
    }

@@

#x <- subset(populationSizes, modelName=="SmoothModelMean-nbinomial-ar1-priors1" & Scenario=="C")
#y <- lm(Estimated~Observed, x)

@@

#table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=10*cutoff, models=modelNames[c(1,3,5)])
#logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(10*cutoff+1), models=modelNames[1])
#logTable2$Failed <- table2$Failed

#table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=cutoff, models=modelNames[c(1,3,5)])
#logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(cutoff+1), models=modelNames[1])
#logTable3$Failed <- table3$Failed

subset(logTable1, Model != "VT")
subset(logTable2, Model != "VT")
subset(logTable3, Model != "VT")

@@

plotPopulationSizesTable_DEPRECATED <- function(logTable) {
  library(reshape2)
  facet_labeller <- function(variable, value) {
    measured <- list(EstTrue=expression(alpha), Slope=expression(beta), R2=expression(R^2), Failed="Failed (%)")
    print(paste0(variable,"=",value))
    if (variable=="variable") return(measured[value])
    if (variable=="Case") return(paste("Case", value))
  }

  #x <- melt(logTable, id.vars=c("Scenario", "Model", "Case"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))
  x <- melt(logTable, id.vars=c("Scenario", "Model"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))

  bestFit <- data.frame(variable=unique(x$variable), y=c(0, 1, 1, 0))
  errorBars <- x
  errorBars$value <- NA
  #errorBars$value[errorBars$variable=="Slope"] <- logTable$Slope
  #errorBars$qmin[errorBars$variable=="Slope"] <- logTable$Slope-logTable$SlopeSD
  #errorBars$qmax[errorBars$variable=="Slope"] <- logTable$Slope+logTable$SlopeSD
  errorBars$value[errorBars$variable=="EstTrue"] <- logTable$EstTrue
  errorBars$qmin[errorBars$variable=="EstTrue"] <- logTable$EstTrueMin
  errorBars$qmax[errorBars$variable=="EstTrue"] <- logTable$EstTrueMax

  p <- ggplot(x, aes(Scenario, value, group=Model)) +
    geom_hline(data=bestFit, aes(yintercept=y), color="darkgray") + 
    geom_errorbar(data=errorBars, aes(Scenario, group=Model, ymax=qmax, ymin=qmin), position=position_dodge(width=.7), colour="darkgray") +
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) + ylab("") +
    #facet_grid(variable~., scales="free_y", labeller=facet_labeller) +
    facet_wrap(~variable, scales="free_y", nrow=2) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=10),
                                        legend.position="bottom",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, 0, -.5), units="line"),  #top, right, bottom, and left margins
                                        legend.margin=unit(-1.5, units="line"))# , legend.key=element_rect(fill="transparent"))

  # Expand y-axis 100 for Failed
  x <- data.frame(Scenario="A", Model="FMP", variable="Failed", value=100)
  p <- p + geom_blank(data=x, aes(x=Scenario, y=value, group=Model))

  p <- facet_wrap_labeller(p, labels=c(expression(alpha), Slope=expression(beta), R2=expression(R^2), Failed="Failed (%)"))

@@

  p1 <- x %>% filter(variable=="EstTrue") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=0), aes(yintercept=y), color="darkgray") + 
    geom_errorbar(data=errorBars, aes(Scenario, group=Model, ymax=qmax, ymin=qmin), position=position_dodge(width=.7), colour="darkgray") +
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(alpha)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line")) #top, right, bottom, and left margins
  g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, just="left", gp=gpar(fontsize=10)))

  p2 <- x %>% filter(variable=="Slope") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=1), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(beta)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line"))
  g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, just="left", gp=gpar(fontsize=10)))

  p3 <- x %>% filter(variable=="R2") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=1), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(R^2)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line"))
  g3 <- arrangeGrob(p3, main=textGrob("c)", x=0.01, just="left", gp=gpar(fontsize=10)))

>>>>

#studyArea <- FinlandStudyArea$new(context=context)$setup(tolerance=0.001)
boundaryDF <- ggplot2::fortify(FinlandWTCStudy(context=context, response="canis.lupus")$studyArea$boundary)
cutoff <- c(1,1000)
```

@@

for (scenario in scenarios) {
  mss <- getMSS(scenario, nSurveyRoutes=500)
  study <- mss$study
  tracks <- study$loadTracks(iteration=iterations[i])
  intersections <- tracks$countIntersections(surveyRoutes=study$surveyRoutes, save=F)

@@

@@

#window <- c(3.375, 3.4, 6.9, 6.925)*1e6
window <- (c(3.425, 3.45, 6.95, 6.975)+c(-.01,.01,-.01,.01)*9)*1e6
habitatRaster <- crop(study$studyArea$habitat, extent(window))
z <- sampleRegular(habitatRaster, 10000, asRaster=TRUE)
habitatData <- as.data.frame(rasterToPoints(z))
colnames(habitatData) <- c("x","y","z")
habitatData$scenario <- factor("E", levels=scenarios)
habitatData2 <- habitatData
habitatData2$scenario <- factor("F", levels=scenarios)
habitatData <- rbind(habitatData, habitatData2)

@@

habitatData$x <- habitatData$x / 1000
habitatData$y <- habitatData$y / 1000
trackData$long <- trackData$long / 1000
trackData$lat <- trackData$lat / 1000
surveyRoutesData$long <- surveyRoutesData$long / 1000
surveyRoutesData$lat <- surveyRoutesData$lat / 1000
window <- window / 1000

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.4) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray55","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_ms() + theme(panel.border=element_rect(fill="transparent")) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)") +
  theme(legend.position="none", panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), panel.grid.major=element_blank(), plot.margin=unit(c(0,0.1,0,0), "lines")) # top, right, bottom, and left  
saveFigure(p, "manuscript-figure-1.png", width=17, height=15, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-1.pdf", width=17, height=15, dpi=300)

@@

@@

#x<-data.frame(scenario="C", iteration=as.integer(3), stringsAsFactors=F)
getAgentLocations = function(scenarios, modelName, iterations, years) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, years) {
    study <- getStudy(scenario=x$scenario)
    tracks <- study$loadTracks(iteration=x$iteration)
    tracks$tracks <- subset(tracks$tracks, year %in% years & yday<59)
    intersections <- study$loadIntersections(iteration=x$iteration)

@@

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE, weightHabitats=F) {
  ddply(data.frame(scenario=scenarios, year=rep(year, length(scenarios)), iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    withHabitatWeights <- if (weightHabitats && substr(x$scenario, 1, 1) %in% c("E","F")) T else F
    study <- getStudy(scenario=x$scenario, withHabitatWeights=withHabitatWeights)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()
    estimates$data <- subset(estimates$data, year == x$year)

    density <- estimates$getPopulationDensity(.parallel=T)
    density <- if (withHabitatWeights) {
      habitatWeights <- study$getHabitatWeights(iteration=x$iteration)
      habitatWeightsRaster <- habitatWeights$getWeightsRaster(save=F)
      density$weight(habitatWeightsRaster)
    } else wdensity <- density$copy()

    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- x$year

    return(density)
  }, modelName=modelName, sd=sd)
}

@@

wdensitiesScaled$x <- wdensitiesScaled$x / 1000 - 3000
wdensitiesScaled$y <- wdensitiesScaled$y / 1000 - 6000
densitiesScaled$x <- densitiesScaled$x / 1000 - 3000
densitiesScaled$y <- densitiesScaled$y / 1000 - 6000
boundaryDF$lat <- boundaryDF$lat / 1000 - 6000
boundaryDF$long <- boundaryDF$long / 1000 - 3000
agents$x <- agents$x / 1000 - 3000
agents$y <- agents$y / 1000 - 6000
limits@xmin <- limits@xmin / 1000 - 3000
limits@ymin <- limits@ymin / 1000 - 6000
limits@xmax <- limits@xmax / 1000 - 3000
limits@ymax <- limits@ymax / 1000 - 6000
surveyRoutes$x <- surveyRoutes$x / 1000 - 3000
surveyRoutes$y <- surveyRoutes$y / 1000 - 6000
gridTemplate@extent@xmin <- round(gridTemplate@extent@xmin / 1000) - 3000
gridTemplate@extent@ymin <- round(gridTemplate@extent@ymin / 1000) - 6000
gridTemplate@extent@xmax <- round(gridTemplate@extent@xmax / 1000) - 3000
gridTemplate@extent@ymax <- round(gridTemplate@extent@ymax / 1000) - 6000

p1 <- ggplot(wdensitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(data=densitiesScaled, aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2)))), trans="log10",
                       breaks=trans_breaks("log10", function(x) 10^x),
                       labels=trans_format("log10", math_format(10^.x))
                       ) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="black", size=0.5) +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01), breaks=pretty_breaks(n=3)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_ms() +
  theme(legend.position="bottom", legend.margin=unit(-1, units="line"), legend.title=element_text(size=10), legend.text=element_text(size=10)) + #top, right, bottom, and left margins
  theme(strip.background=element_blank(), panel.background=element_rect(fill="transparent", colour=NA), panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)")
g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g1, "manuscript-figure-2a.png", width=17, height=8.07, dpi=200) # draft quality
saveFigure(g1, "manuscript-figure-2a.pdf", width=17, height=8.07, dpi=300)

xlabels <- seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5/1000)
xlabels[c(2,4,6,7)] <- ""
p2 <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey", size=0.5) +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5/1000), expand=c(0.01,0.01), labels=xlabels) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5/1000), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_ms() +
  theme(panel.grid.major=element_line(colour="grey")) + #top, right, bottom, and left margins
  theme(strip.background=element_blank(), panel.background=element_rect(fill="transparent", colour=NA), panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), legend.position="none", axis.ticks=element_line(colour="grey", size=0.2)) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)")
g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g2, "manuscript-figure-2b.png", width=17, height=7.2, dpi=200) # draft quality
saveFigure(g2, "manuscript-figure-2b.pdf", width=17, height=7.2, dpi=300)

p <- arrangeGrob(g1, g2, heights=c(8.07, 7.2)/(8.07+7.2))
saveFigure(p, "manuscript-figure-2.png", width=17, height=8.07+7.2, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-2.pdf", width=17, height=8.07+7.2, dpi=300)
```

@@

getPopulationSizes <- function(scenarios, modelNames, populationSizeCutoff=Inf) {
  study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
  validation <- Validation(study=study, populationSizeCutoff=populationSizeCutoff)
  populationSizes <- validation$getValidationTemporalPopulationSizes(scenarios=scenarios, modelNames=modelNames)
}

@@

populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames[c(1,3,4,5)])
meanPopulationSizes  <- getMeanPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[c(1,3,5)]))
logPopulationSizes <- getLogPopulationSizes(cutoffPopulationSizes(populationSizes, cutoff, models=modelNames[c(1,3,5)]))
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, models, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate, models) {
    xrows <- nrow(x)
    old <- x
    x <- cutoffPopulationSizes(x, overEstimate, models=models)
    if (nrow(x) == 0) {
      print(old)
      stop("ERROR")
    }

@@

@@

#subset(populationSizes, Scenario=="C" & modelName=="FMPModel")
#subset(populationSizes, Scenario=="B" & modelName=="FMPModel")

@@

@@

  margin <- unit(c(0.1, 0.1, -.75, 0), units="line")

  p1 <- x %>% filter(variable=="EstTrue") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=0), aes(yintercept=y), color="darkgray") + 
    geom_errorbar(data=errorBars, aes(Scenario, group=Model, ymax=qmax, ymin=qmin), position=position_dodge(width=.7), colour="darkgray") +
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(alpha)) +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=margin) #top, right, bottom, and left margins
  g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))

  p2 <- x %>% filter(variable=="Slope") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=1), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(beta)) +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=margin)
  g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))

  p3 <- x %>% filter(variable=="R2") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=1), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(R^2)) +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=margin)
  g3 <- arrangeGrob(p3, main=textGrob("c)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))

  p4 <- x %>% filter(variable=="Failed") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=0), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab("Failed (%)") + ylim(0,100) +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=margin)
  g4 <- arrangeGrob(p4, main=textGrob("d)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))

  legend <- gtable_filter(ggplot_gtable(ggplot_build(p1 + theme(legend.position="bottom", legend.margin=unit(-1, units="line")))), "guide-box")
  lheight <- sum(legend$height)
  theight <- unit(10, "points")
  #p <- arrangeGrob(g1, g2, g3, g4, ncol=2)

  p1 <- arrangeGrob(g1, g3, nrow=2)
  p2 <- arrangeGrob(g2, g4, nrow=2)
  p1 <- arrangeGrob(p1, textGrob("Scenario", x=0.58, gp=gpar(fontsize=10)), heights=unit.c(unit(1, "npc") - theight, theight))
  p2 <- arrangeGrob(p2, textGrob("Scenario", x=0.57, gp=gpar(fontsize=10)), heights=unit.c(unit(1, "npc") - theight, theight))
  p <- arrangeGrob(p1, p2, ncol=2)
